\newpage
\addcontentsline{toc}{chapter}{Abstract}
\thispagestyle{empty}
\hoffset=0mm
% The abstract goes here
\begin{center}
    {\Large \bf Abstract}
\end{center}
\begin{spacing}{1.35}

\par
Mobile sector is getting developed in tremendous speed in the latest decades. More and more new devices are introduced as well as new frameworks and programming languages for developing applications for mobile platforms. As testing is one of the most important part in product development lifecycle, it needs to respond to these challenges with fast, effective and cost-efficient process. Test execution automation has been proven to be very effective approach for reducing testing time, but there is still enough opportunities to improve in current testing processes, such as static test suites which are difficult and time consuming to maintain, also reducing the time required to achieve complete test execution automation and many others. \acrlong{mbt} raises test automation to new level with providing opportunity, not only to automate test execution, but also test generation process. It addresses above mentioned issues by creating unique tests for each test run using the behavioral models of \acrlong{aut}. This is the valid reason for Brainloop, to try out \acrlong{mbt} for one of its mobile application called \acrlong{bsc} and see the results providing information about the improvements in software quality and cost-effectivenes of this approach, as well as the vision for effective integration of \acrlong{mbt} into its agile environment.

\par
In the first phase of this thesis we did literature review for identifying the most suitable tool for applying \acrlong{mbt} for \acrlong{bsc} according to requirements from Brainloop. The chosen tool was open-source tool called Graphwalker which was developed and is being used in Spotify. 

\par
Next phase was dedicated to applying yEd Graph Editor, free software for creating models for Graphwalker, for modeling the behaviour of \acrlong{bsc} in an abstracted manner. Overall, 33 models were creating for describing significant part of the functionality in \acrlong{bsc}, but due to timing and complexity reasons some of the functionality were omitted during modeling.

\par
In the last phase we generated test sequences with different coverage criteria and executed tests against one device manually. As a result, we detected some issues which were not detected during the current testing process. We also provided the vision of gradually integrating \acrlong{mbt} into current agile scrum process applied by Brainloop.

\end{spacing}
