
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\thispagestyle{empty}
\hoffset=0mm
\begin{center}
    {\Large \bf Acknowledgement}
\end{center}

\vspace{1cm}

I am extremely grateful to my parents, who even in their hardest times, gave the highest priority towards the education of their children. I would like to take this opportunity to thank them for making my studies at TUM possible. This is undoubtedly their achievement.

I would like to express my sincerest gratitude to Prof. Dr. Jan Kretinsky for supervising my thesis at the chair for Foundations of Software Reliability and Theoretical Computer Science, Department of Informatics, Technical University of Munich. 

I am deeply thankful to Pranav Ashok, my advisor at the chair for Foundations of Software Reliability and Theoretical Computer Science, Department of Informatics, Technical University of Munich, and Ulrich Sebastian Ganz, Head of Engineering Clients, BDRS and Release Engineering in Brainloop, my supervisor at Brainloop, for believing in me and providing me with this unique opportunity to write the master thesis on this specific topic. Also for the motivation, continuous encouragement and appreciation and interesting inputs that were vital for successful completion of my master thesis.

This project would not have been possible if it was not for my spouse and sisters who have always provided unwavering support in all my endeavours.

Finally, this acknowledgement would be incomplete without a mention of my friends and their help with sourcing all the right information and various resources during my research.

